---
title: "Presentation using Shiny"
author: "Csaba Iranyi"
date: "July 1, 2019"
output: ioslides_presentation
---

## Pixels Per Inch (PPI) Calculator

The PPI Calculator finds pixels per inch (PPI).

### What is PPI

PPI is a measure of pixel density or resolution of a computer screen, television screen or other display device.  
  
Pixels per inch indicates how many pixels are in a 1 inch line on a display.  
  
The PPI will be the same whether it's a horizontal or vertical or diagonal inch because pixels are square and therefore symmetric.

## Calculator Usage

Enter the width of screen in pixels.  
  
Enter the height of screen in pixels.  
  
Choose the diagonal (in inches) with the slider.
  
The app calculates the PPI value immediately. 

## Sample

Width of the screen in pixels:
```{r echo = TRUE}
screen.width = 1920
```

Height of the screen in pixels:
```{r echo = TRUE}
screen.height = 1080
```

Diagonal of the screen in inches:
```{r echo = TRUE}
screen.diagonal = 10.5
```

Calculate the PPI value:
```{r echo = TRUE, comment = ""}
round(sqrt(screen.width^2 + screen.height^2) / screen.diagonal)
```

## Links

### The calculator app is available at: 
- https://iranyics.shinyapps.io/PPI_calculator/

### Further readings:
- https://en.wikipedia.org/wiki/Pixel_density
