---
title: "R Markdown and Leaflet: Course Project"
author: "Csaba Iranyi"
date: "06.28.2019"
output: 
  html_document:
    theme: yeti
    highlight: tango
    df_print: kable
    code_folding: hide
---

## The best indian restaurants in Budapest {.tabset .tabset-fade}

Budapest's Indian restaurants aren't about to set the food world on fire, but this shouldn't surprise you: the city has a small Indian expat community, and few locals seek out Indian food (though tourism from India is rising). 
  
The below restaurants serve the usual suspects of northern Indian fare, including reliably prepared tandoori chicken, korma dishes, butter chicken, biryani, saag paneer, and dal makhani.

### List of restaurants

```{r restaurant}

# Restarurants data
restaurants <- data.frame(
  "Name" = c("<font size=\"+1\">Indigo Indian Restaurant</font>",
             "<font size=\"+1\">Rajkot Palace</font>",
             "<font size=\"+1\">Curry House</font>",
             "<font size=\"+1\">Taj Mahal</font>",
             "<font size=\"+1\">Royal Rasoi</font>",
             "<font size=\"+1\">Salaam Bombay</font>",
             "<font size=\"+1\">Bangla Bufe Premium</font>",
             "<font size=\"+1\">MahaRana Indian Ayurvedic Restaurant</font>",
             "<font size=\"+1\">Haveli Indian Restaurant</font>",
             "<font size=\"+1\">Govinda Restaurant</font>",
             "<font size=\"+1\">Pandzsab Tandoori Restaurant</font>",
             "<font size=\"+1\">Swaad Restaurant</font>",
             "<font size=\"+1\">Shalimar</font>"),
  "Address" = c("<a href=\"https://www.google.com/maps/search/?api=1&query=Indigo+Indian+Restaurant+Budapest\">Budapest, Jókai u. 13, 1066</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=Rajkot+Palace+Budapest\">Budapest, Nyáry Pál u. 9, 1056</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=Curry+House+Budapest\">Budapest, Bródy Sándor u. 21, 1088</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=Taj+Mahal+Budapest\">Budapest, Szondi u. 40, 1067</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=Royal+Rasoi+Budapest\">Budapest, Ráday u. 5, 1092</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=Salaam+Bombay+Budapest\">Budapest, Mérleg u. 6, 1051</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=Bangla+Bufe+Premium+Budapest\">Budapest, Akácfa u. 40, 1072</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=MahaRana+Restaurant+Budapest\">Budapest, Hegedűs Gyula u. 7, 1136</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=Haveli+Indian+Restaurant+Budapest\">Budapest, Szinyei Merse u. 1, 1063</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=Govinda+Restaurant+Budapest+Vigyazo+Ferenc\">Budapest, Vigyázó Ferenc u. 4, 1051</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=Pandzsab+Restaurant+Budapest\">Budapest, Pannónia u. 3, 1133</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=Swaad+Restaurant+Budapest\">Budapest, Gömb u. 5, 1139</a>",
                "<a href=\"https://www.google.com/maps/search/?api=1&query=Shalimar+Restaurant+Budapest\">Budapest, Dob u. 53, 1072</a>"),
  "Website" = c("<a href=\"http://indigo-restaurant.hu\">indigo-restaurant.hu</a>",
                "<a href=\"http://rajkotpalace.com\">rajkotpalace.com</a>",
                "<a href=\"http://curry-house.hu\">curry-house.hu</a>",
                "<a href=\"http://tajmahal.hu\">tajmahal.hu</a>",
                "<a href=\"http://royalrasoi.hu\">royalrasoi.hu</a>",
                "<i>No website</i>",
                "<i>No website</i>",
                "<a href=\"http://maharana.hu\">maharana.hu</a>",
                "<a href=\"http://haveli.hu\">haveli.hu</a>",
                "<a href=\"http://govindabudapest.business.site\">govindabudapest.business.site</a>",
                "<a href=\"http://indiaietterem.hupont.hu\">indiaietterem.hupont.hu</a>",
                "<a href=\"http://swaad.hu\">swaad.hu</a>",
                "<a href=\"http://shalimar.hu\">shalimar.hu</a>"),
  "Rating" = c("#121",
               "#148",
               "#208",
               "#211",
               "#275",
               "#308",
               "#337",
               "#501",
               "#516",
               "#528",
               "#643",
               "#744",
               "#751"),
  "latitude" = c(47.507122,
                 47.490554,
                 47.492852,
                 47.510788,
                 47.487906,
                 47.499555,
                 47.500082,
                 47.512656,
                 47.510286,
                 47.501137,
                 47.513246,
                 47.532872,
                 47.501023),
  "longitude" = c(19.059445,
                  19.055953,
                  19.067327,
                  19.064574,
                  19.062680,
                  19.048725,
                  19.065572,
                  19.052942,
                  19.069438,
                  19.048051,
                  19.051597,
                  19.071995,
                  19.065126))

restaurants[, 1:4]
```

### Locations on Map

```{r echo = FALSE}
library(leaflet)
```

```{r message = FALSE, out.width = "100%", fig.height = 10}

# Icons
icons <- awesomeIcons(
  icon = "fa-cutlery",
  iconColor = "#eeeeee",
  library = "fa",
  markerColor = "purple"
)

# Map
restaurants[, 5:6] %>% 
leaflet() %>% 
addProviderTiles("OpenStreetMap.Mapnik",) %>%
setView(lat = 47.501717, lng = 19.058479, zoom = 14) %>%
addAwesomeMarkers(popup = paste(restaurants$Name, restaurants$Website, sep = "<br/>"), icon = icons, labelOptions = c(opacity = 0.5, interactive = TRUE ))
```
